---
title: "Customer Churn Analysis"
author: "YOUR NAME HERE"
date: "7/20/2021"
output: html_document
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
```

## Data Read

```{r}
churn <- read_csv(here("Data", "churn.csv"))
```

```{r}
str(churn)
summary(churn)
glimpse(churn)
```


## Data Exploration

```{r}
churn %>%
  ggplot() +
  geom_histogram(aes(x = Tenure))
```


```{r}
## Explore some categorical or discrete variables

churn %>%
  count(Geography)

churn %>%
  ggplot() +
  geom_bar(aes(x = Geography))

```

## Data Cleaning


```{r}
churn <- churn %>%
  mutate(
    Geography = factor(Geography),
    Gender = factor(Gender),
    HasCrCard = factor(HasCrCard,
                       levels = c("0", "1"),
                       labels = c("No", "Yes")),
    IsActiveMember = factor(IsActiveMember,
                       levels = c("0", "1"),
                       labels = c("No", "Yes")),
    Exited = factor(Exited,
                       levels = c("0", "1"),
                       labels = c("No", "Yes")),
  )
```

## Data Summaries

1. What are the mean and median account balances among customers in this dataset?

```{r}
churn %>%
  summarize(
    mean(Balance),
    median(Balance)
  )
```


2. What are the mean values of: age, account balance, and salary?

```{r}
churn %>%
  summarize(
    across(c(Age, Balance, EstimatedSalary),
           list(mean))
  )
```

3. Among customers in the USA, what is the average credit score?

```{r}
churn %>%
  filter(Geography == "USA") %>%
  summarize(mean(CreditScore))
```

Among customers in France, what is the average credit score?

```{r}
churn %>%
  filter(Geography == "France") %>%
  summarize(mean(CreditScore))
```



4. What country are the customers with the top three highest balances from?

```{r}
churn %>%
  top_n(3, Balance) %>%
  select(Geography, Balance)
```


5. Do the average salaries differ between those with credit cards and those without?

```{r}
churn %>%
  group_by(HasCrCard) %>%
  summarize(mean(EstimatedSalary))
```


6. Is there a difference in gender distribution of customers who have exited the bank?

```{r}
churn %>%
  count(Gender, Exited)
```



## More Visualization

```{r}
## Comparing categorical variables

churn %>%
  ggplot() +
  geom_bar(aes(x = Gender,
               fill = Exited))

churn %>%
  ggplot() +
  geom_bar(aes(x = Gender,
               fill = Exited),
           position = "fill")


churn %>%
  ggplot() +
  geom_bar(aes(x = Gender,
               fill = Exited),
           position = "dodge")


churn %>%
  ggplot() +
  geom_bar(aes(x = Gender,
               fill = Exited)) +
  facet_wrap(~Geography)
```

```{r}
## comparing a categorical and a quantitative

churn %>%
  ggplot() +
  geom_boxplot(aes(x = Geography,
                   y = EstimatedSalary))


churn %>%
  ggplot() + 
  geom_density(aes(x = Geography,
                   y = EstimatedSalary),
               alpha = 0.5)

```


```{r}
churn %>%
  ggplot() + 
  geom_point(aes(x = EstimatedSalary,
                   y = Balance)) +
  theme_classic()

```


## Pivoting

1. Find the average salary of each gender in each country.

```{r}
sal_by_country <- churn %>%
  group_by(Gender, Geography) %>%
  summarize(
    mean_sal = mean(EstimatedSalary)
  )

sal_by_country
```


2. Pivot your data frame from (1) so that there is one column for each gender identity.

```{r}
sal_by_country <- sal_by_country %>%
  pivot_wider(
    names_from = Gender,
    values_from = mean_sal,
    names_prefix = "av_sal_"
  )

sal_by_country
```


3. Create a new column showing the difference between female-identifying and male-identifying average salaries.

```{r}
sal_by_country <- sal_by_country %>%
  mutate(
    sal_diff = av_sal_Male - av_sal_Female
  )
```



## Joining

Repeat the above, this time for balances rather than salaries.

```{r}
bal_by_country <- churn %>%
  group_by(Gender, Geography) %>%
  summarize(
    mean_bal = mean(Balance)
  ) %>%
   pivot_wider(
    names_from = Gender,
    values_from = mean_bal,
    names_prefix = "av_bal_"
  ) %>%
  mutate(
    bal_diff = av_bal_Male - av_bal_Female
  )

```


Join the two datasets by country name.

```{r}
sal_by_country %>%
  full_join(bal_by_country)
```



## Your own analysis

Choose one of the following research questions to address with a beautiful plot (or make up your own).  Write up your results in a **new** R Markdown file, in your **new** project.

* How does the relationship between age and churn (exit) differ by gender/country?

* Is a customer with a credit card considered "desirable"?  For example, do they stay with the bank longer?  Are they less likely to exit? Do they use more bank products?

* How does age impact customer behavior?  That is, is the impact of other qualities (balance, salary, etc) on customer tenure and/or churn different across ages?

