---
title: "Classification with KNN and Logistic Regression"
resource_files:
- appforthat.jpg
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightLines: yes
      highlightStyle: github
      countIncrementalSlides: false
      ratio: '16:9'

---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, digits = 4, scipen=999)
library(tidyverse)
library(tidymodels)
library(flair)
library(kknn)
library(glmnet)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
style_mono_light(
  base_color = "#26116c",
  text_bold_color = "#fd5e53",
  title_slide_text_color = "#fff8e7",
  background_color = "#fff8e7",
  header_font_google = google_font("Roboto"),
  text_font_google   = google_font("Roboto Condensed"),
  code_font_google   = google_font("Droid Mono")
)
```

```{css, echo = FALSE}
.red{ color: red; }
.blue{ color: blue; }
.huge {
  font-size: 200%;
}
.large {
  font-size: 150%;
}
.tiny {
  font-size: 50%;
}
```

---

# Other Data Science Skills

* Writing your own custom functions

* Iteration and functional programming with the {purrr} package

* Interactive web apps with {Shiny}

* More automated reporting with R Markdown

* Connecting to databases with {obdc} and {dbplyr}

---
# Other Data Viz Skills

* More geometries:  https://www.data-to-viz.com/

* Custom ggplot themes  (https://rpubs.com/mclaire19/ggplot2-custom-themes)

* Maps with {leaflet}

* Animated plots with {gganimate}


---

# Other Modeling Skills

* Many more ML algorithms:  www.tidymodels.org

* *Tuning* parameters of a model: https://juliasilge.com/blog/sf-trees-random-tuning/

* *Clustering* and *Dimension Reduction*

* Putting models into production with {plumbeR} and Docker

* Try out some Kaggle competitions!

---
# Where to go from here:

* Analyze the `application_record.csv` dataset, email me your results!  (kelly@bodwin.us)

--

* R for Data Science:  https://r4ds.had.co.nz/

--

* Julia Silge's blog: https://juliasilge.com/blog/

--

* Follow Kelly (@KellyBodwin) and Hunter (@hglanz) on twitter

--

* Drop-in consulting hours for help:  https://calendly.com/kbodwin/consulting?month=2021-07



